---
title: "a4a Stock Assessment Report"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
params:
  stk: NA
  idx: NA
  fit: NA
  comp_stk: NA
---

```{r setup, include=FALSE}
library(FLa4a)
library(ggplotFL);theme_set(theme_bw())
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 9, fig.height = 7)

# Extract objects from params
stk <- params$stk
idx <- params$idx
fit <- params$fit
stk.sim <- stk + simulate(fit, nsim = 1000)
```

# Assessment Results {.tabset .tabset-pills}

## Data Input

* Years range of the stock: `r range(stk)['minyear']` : `r range(stk)['maxyear']`

* Plusgroup: `r range(stk)['plusgroup']`

* Fbar range: `r range(stk)['minfbar']` : `r range(stk)['maxfbar']`

```{r conditional-warning, echo=FALSE, results='asis'}                   
  sopchk <- computeCatch(stk)/catch(stk)
                                                                                                     
    # if (any(abs(as.numeric(sopchk) - 1) > 0.0001, na.rm = TRUE)) {                                                      
    #   cat('                                                                  
    # <div class="alert alert-danger">                                         
    #   ⚠️ WARNING: Your have not SoP corrected your stock                                        
    # </div>                                                                   
    # ')
    # }
 if (any(abs(as.numeric(sopchk) - 1) > 0.0001)) {
   cat('<span style="color: red; font-weight: bold;">You have not SoP corrected your stock</span>')
 }


```


```{r data-input, warning = FALSE}
# Combine into a single FLQuants object and convert to a data.frame for ggplot
df_cld <- as.data.frame(FLQuants(
  Catch = catch(stk),
  Landings = landings(stk),
  Discards = discards(stk)
))

ggplot(df_cld, aes(x = year, y = data, color = qname)) +
  geom_line(linewidth = 1) +
  scale_color_viridis_d(option = "turbo") +
  theme_bw(base_size = 12) +
  labs(
    title = "Catch, Landings, and Discards over Time",
    x = "Year",
    y = "Tonnage",
    color = ""
  ) +
  theme(legend.position = "bottom")
```

### Catch-at-Age

```{r catch-at-age, warning=FALSE}
age_breaks <- as.numeric(range(stk)["min"]):as.numeric(range(stk)["max"])

ggplot(as.data.frame(catch.n(stk)), 
       aes(x = as.numeric(as.character(age)), 
           y = data, 
           color = as.numeric(as.character(year)),              
           group = as.factor(year))) +
  geom_line(alpha = 0.85) +
  scale_color_viridis_c(option = "turbo") +
  labs(title = "Catch-at-Age", x = "Age", y = "Numbers", color = "Year") +
  theme_bw(base_size = 9) +
  theme(legend.position = "right") +
  scale_x_continuous(breaks = age_breaks)
```

### Index by age

```{r index-by-age, warning = FALSE}
plot(index(idx)[[1]])
```

### Weight-at-Age

```{r weight-at-age, warning=FALSE}
ggplot(as.data.frame(stock.wt(stk)), 
       aes(x = as.numeric(as.character(age)), 
           y = data, 
           color = as.numeric(as.character(year)),              
           group = as.factor(year))) +
  geom_line(alpha = 0.85) +
  scale_color_viridis_c(option = "turbo") +
  labs(title = "Weight-at-Age (Stock)", x = "Age", y = "Weight", color = "Year") +
  theme_bw(base_size = 9) +
  theme(legend.position = "right") +
  scale_x_continuous(breaks = age_breaks)
```

### Maturity and Natural Mortality

```{r mat-and-m, fig.width=10, fig.height=4, warning=FALSE}

library(kableExtra)
# Extract just the first year since maturity and M are constant
df_mat <- as.data.frame(mat(stk)[, 1])
df_m   <- as.data.frame(m(stk)[, 1])

p_mat <- ggplot(df_mat, aes(x = as.numeric(as.character(age)), y = data)) +
  geom_line(linewidth = 1, color = "#2c7bb6") +
  geom_point(color = "#2c7bb6", size = 2) +
  labs(title = "Maturity-at-Age", x = "Age", y = "Proportion Mature") +
  theme_bw(base_size = 10) +
  scale_x_continuous(breaks = age_breaks)

p_m <- ggplot(df_m, aes(x = as.numeric(as.character(age)), y = data)) +
  geom_line(linewidth = 1, color = "#d7191c") +
  geom_point(color = "#d7191c", size = 2) +
  labs(title = "Natural Mortality-at-Age (M)", x = "Age", y = "M") +
  theme_bw(base_size = 10) +
  scale_x_continuous(breaks = age_breaks)

# Plot side by side
gridExtra::grid.arrange(p_mat, p_m, ncol = 2)
```

## Stock Summary

### Submodel configuration

```{r submodels-table}
    strip_formula <- function(mod) {
        as.formula(paste(deparse(formula(mod)), collapse = " "))
    }
    
    fmod_base  <- strip_formula(fmodel(fit))
    srmod_base <- strip_formula(srmodel(fit))
    n1mod      <- strip_formula(n1model(fit))
    qmod       <- lapply(as.list(qmodel(fit)), strip_formula)
    vmod       <- lapply(as.list(vmodel(fit)), strip_formula)
  
    format_form <- function(x) {
      paste(deparse(x), collapse = " ")
    }

    submodels_df <- data.frame(
      Component = c(
        "Fishing Mortality (fmodel)", 
        "(Stock) Recruitment (srmodel)", 
        "Initial N (n1model)", 
        paste("Catchability (qmodel):", names(qmod)),
        paste("Variance (vmodel):", names(vmod))
      ),
      Formula = c(
        format_form(fmod_base),
        format_form(srmod_base),
        format_form(n1mod),
        sapply(qmod, format_form),
        sapply(vmod, format_form)
      )
    )
  
    
kable(submodels_df, format = "html", col.names = c("Submodel Component", "Formula")) |>           
      kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE) |>    
      column_spec(1, bold = TRUE, width = "18em") |>
      column_spec(2, monospace = TRUE, color = "#2c7bb6")


```

### Summary Plots (F, SSB, Catch, Recruits)

```{r summary-plot}
plot(stk.sim)
```

```{r summary-table}

summary_df <- data.frame(
      Year = as.numeric(dimnames(stk)$year),
      Recruits = round(as.numeric(iterMedians(rec(stk.sim))), 0),
      SSB = round(as.numeric(iterMedians(ssb(stk.sim))), 0),
      Catch = round(as.numeric(iterMedians(catch(stk.sim))), 0),
      Fbar = round(as.numeric(iterMedians(fbar(stk.sim))), 3)
    )
kableExtra::kable(summary_df)
```

### Submodel plots

```{r harvest-q--wire}
w1 <- wireframe(data ~ age + year, data = as.data.frame(harvest(fit)), drape = TRUE,
          main="Fishing mortality", screen = list(x = -90, y=-45),
          col.regions = colorRampPalette(c("blue", "yellow"))(100))
          qhat <- predict(fit)$qmodel[[1]]
w2 <- wireframe(data ~ age + year, data = as.data.frame(qhat), drape = TRUE,
          main="Catchability", screen = list(x = -90, y=-45),
          col.regions = colorRampPalette(c("blue", "yellow"))(100))

gridExtra::grid.arrange(w1,w2,ncol = 2)
```

```{r catcability-wire}

```

## Diagnostics

### Log Residuals

```{r residuals-plot}
res <- residuals(fit, stk, idx)
plot(res)
```

### Bubble plot

```{r bubble-plot}
bubbles(res)
```

### Quantile plot

```{r quantile-plot}
qqmath(res)
```

### Fitted vs. Observed Catch

```{r fit-obs-plot}
plot(fit, stk)
```


### Fit against indices

```{r q-plot}
plot(fit, idx)
```


### Aggregated catch diagnostics

```{r aggr-catch-diag}
c_d <- computeCatchDiagnostics(fit, stk)
plot(c_d, cex=0.8)
```

### Hindcast

```{r hindcast, error = TRUE}
library(a4adiags)
nyears <- 5
nsq <- 3
hc <- try(a4ahcxval(stk, idx, nyears = nyears, nsq = nsq), silent = TRUE)
if (!inherits(hc, "try-error")) {
  plotXval2(hc$indices)
} else {
  message("a4ahcxval encountered an error and was skipped.")
}
```


## Retrospective plot

```{r retro}
retros <- wmsc::retro(stk,idx,fit,peels = 3, kfrac = 0.5)
pills <- length(retros) - 1 
mohn_ssb <- icesAdvice::mohn(mohnMatrix(retros, ssb), peels = pills)
mohn_f   <- icesAdvice::mohn(mohnMatrix(retros, fbar), peels = pills)

retros[[1]] <- stk.sim
plot(retros) +
  labs(subtitle = sprintf("Mohn's rho: SSB = %.3f  |  Fbar = %.3f", mohn_ssb, mohn_f))

```

```{r reference-points}
# Placeholder for reference points
message("Reference points analysis will be displayed here.")
```

## Comparison Plot

```{r stock-comparison}

if (is(params$comp_stk, "FLStock")) {
      plot(FLStocks("Current Assessment" = stk.sim, "Comparison" = params$comp_stk))
    }

```
